$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-19 paper/paper.tex
Add a bit on recursion

% Do not use italics in definitions and theorems
\spnewtheorem{nidefinition}[definition]{Definition}{\bfseries}{}
\spnewtheorem{nilemma}[lemma]{Lemma}{\bfseries}{}
\spnewtheorem{nitheorem}[theorem]{Theorem}{\bfseries}{}

@@

>>>>

% Do not use italics in definitions and theorems
\spnewtheorem{nidefinition}[definition]{Definition}{}{}
\spnewtheorem{nilemma}[lemma]{Lemma}{\bfseries}{}
\spnewtheorem{nitheorem}[theorem]{Theorem}{\bfseries}{}

@@

\subsection{On recursion}
\todo{put somewhere}

Recursion can be added to a resource-algebra-agnostic type system with the following rule:
\begin{mathpar}
  \inferrule
  {\types{\gamma}{\Gamma}{P}{\Gamma}}
  {\types{\gamma}{\Gamma}{!P}{\Gamma}}
\end{mathpar}
That is, if a process consumes no resources (e.g. they are shared), then the process can be executed infinitely many times.
To show subject congruence, one has to prove that $P \eqeq \comp{P}{!P}$ preserves types in both directions.
In our setting, that means showing that $\types{\gamma}{\Gamma}{\comp{P}{!P}}{\Delta}$ then $\types{\gamma}{\Gamma}{!P}{\Delta}$.
Eliminating the hypothesis gives $\types{\gamma}{\Gamma}{P}{\Xi}$ and $\types{\gamma}{\Xi}{!P}{\Delta}$, eliminating the latter unifies $\Xi$ and $\Delta$ resulting in $\types{\gamma}{\Xi}{P}{\Xi}$.
To satisfy the goal $\types{\gamma}{\Gamma}{!P}{\Xi}$, one has to show that $\Gamma$ and $\Xi$ are equivalent too.
Note that the process $P$ does not syntactically restrict the types of the channels created within $P$.
That means that within the typing derivations $\types{\gamma}{\Gamma}{P}{\Xi}$ and $\types{\gamma}{\Xi}{P}{\Xi}$ one can create channels that transmit different amounts of data in $\Gamma$ and in $\Xi$, which are then not necessarily the same anymore.
